Mathematical Aspects of the Capital Market

### 2017-08-01 phd/MyThesis.tex
Revised the importance sampling paper.
Added the paper with Anja to the thesis.
Debugged the program for finding M.

\input{Preamble}
\usepackage[numbers,sort&compress]{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}

\newtheorem{case}{case}

%% \usepackage[toc,page]{appendix}
\usepackage{appendix}
\graphicspath{
        {../papers/FX/}{../papers/Jeffrey1/}
        {../papers/DavisMikoschHeinyXie/}
}

@@

This thesis is about vanity of life.

@@

Thank you all for various things.
\bigskip

@@

\def\phdthesis{1}
\input{Chapterintroduction}
%------------------------------------------------------------------------------------
\input{ChapterTailParameters}
\input{ChapterImportanceSampling}
\input{Chapterextremes}

@@

%for print version only
\newpage
\leavevmode\thispagestyle{empty}
\phantom{bla}
\end{document}

>>>>

\input{Preamble}
\input{../physics_common}

\usepackage[numbers,sort&compress]{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{appendix}
\graphicspath{
        {../papers/FX/}{../papers/Jeffrey1/}
        {../papers/Anja/}
        {../papers/DavisMikoschHeinyXie/}
}

@@

This thesis is about heavy-tailed time series.

@@

I owe my gratitude to many people and especially to my supervisors Prof. Mikosch and Prof. Collamore.
\bigskip

@@

\def\phdthesis{1}
\input{Chapterintroduction}
%------------------------------------------------------------------------------------
\input{ChapterTailParameters}
\input{ChapterImportanceSampling}
\input{Chapterextremes}
\input{ChapterBernoulli}

@@

%for print version only
\newpage
\leavevmode\thispagestyle{empty}
\phantom{bla}

\end{document}
